%% metadata.tex
%%
%% Metainformation for the document
%%
\subject{
	% the subject of your work e.g. Diploma, Großer Beleg ...
	Großer Beleg
}

\title{
	% the title of your works
	Graphical Support for the Design and Evaluation of Configurable Logic Blocks
}

\author{
	% Full name of the author
	Fredo Erxleben
}

\date{
	% the date of publication
	\today
}

\newcommand{\supervisingprof}{
	% the name of your supervising professor
	Prof. Dr.-Ing. habil. Rainer G. Spallek
}

\newcommand{\supervisor}{
	% the name of your supervisor
	Dr.-Ing. Thomas B. Preußer
}

\newcommand{\bornat}{
	% the authors date of birth
	30th\ April\ 1987
}

\newcommand{\bornin}{
	% the authors place of birth
	Blankenburg\,(Harz)
}

\newcommand{\matriculation}{
	%the authors matriculation number
	33\,00\,664
}

\newcommand{\makeabstract}{
	%% put your abstract here
	\paragraph{Abstract}
	Developing a tool supporting humans to design and evaluate \gls{clb}-based circuits requires a lot of know-how and research from different fields of computer science.
	In this work, the newly developed application \emph{q2d}, especially its design and implementation will be introduced as a possible tool for approaching \gls{clb} circuit development with graphical \gls{ui} support.
	Design decisions and implementation will be discussed and a workflow example will be given.
	
	\vspace{4cm}	
	
	\paragraph{Thanks to\dots}
	\begin{itemize}
	\renewcommand{\labelitemi}{\dots}
	\item \emph{Dr. Thomas Peußer}, for letting me occupy a chair in his office, providing a \emph{C/C++} interface for \gls{quantor} using his own parser \emph{wisent} and being a great supervisor.
	
	\item \emph{Dipl.-Inf. Marcus Hähnel}, who offered a lot of advice regarding proper \emph{C++} and \gls{qt}, did code reviews, beta tests and improved the applications build script to be more user friendly.
	
	\item \emph{(Soon to be Dipl.-Minf.) Paula Schöley}, for lengthy discussions about \glspl{ui}, human-machine interaction as well as human perception of shapes and colors. 

	\item \emph{my family and friends}, helping me to keep my feet on the ground

	\item \emph{Krümelchen}, helping me to keep my head in the clouds.
	\end{itemize}
}